Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-06 ms.tex
Minor improvements to text in section 3.1

property that we assume to determine the galaxy HOD is halo formation time. $A_{\rm cen,sat}=0$ means that there is no 
assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally 
correlated (anticorrelated) with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. 
If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 

@@

A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.

We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
that the number of MCMC samples they included in their analysis was 
insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
Additionally, we have recreated qualitatively similar behavior by considering only small subsets of our 
full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
of the discrepancies between our work and that of \citet{zehavi_etal11}.

Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
average and $\alpha$ is the power-law index describing the dependence of average satellite 
number on halo mass. Increasing $M_1$ decreases the number of satellites in large halos 
by placing satellites preferentially in halos of larger mass. An increase in $\alpha$ can partly 
compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
grows with halo mass, leading to a larger number of satellites in high-mass halos.

>>>>

property that we assume to determine the galaxy HOD is halo concentration. $A_{\rm cen,sat}=0$ means that there is no 
assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that galaxy abundance is maximally 
correlated (anticorrelated) with halo concentration at fixed $\mvir.$ Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 
If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, then the model used to interpret the data 

@@

A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. 
Therefore, on these intuitive grounds alone it seems likely that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.

Additionally, we have confirmed with a subset of the authors of \citet{zehavi_etal11} 
that the number of MCMC samples they included in their analysis was 
insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
(Z. Zheng \& I. Zehavi, private communication). The analysis of \citet{zehavi_etal11} 
used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
Additionally, we have recreated qualitatively similar behavior by considering only small subsets of our 
full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
of the discrepancies between our work and that of \citet{zehavi_etal11}.

Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
average, and $\alpha$ is the power-law index describing the dependence of average satellite 
number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos 
by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly 
compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
grows with halo mass.
